\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{datetime}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{Gerbe AI: Review Summary and Action Roadmap}
\author{Internal Research Steering Group}
\date{\today}

\begin{document}
\maketitle

\section*{Executive Snapshot (\(\approx 45\,\text{s}\) read)}
Gerbe~AI elevates drift / skew detection from pair--wise to \(k\)-way interactions by modelling an ML pipeline as a \emph{metrically--enriched category} and searching for \emph{non--vanishing \(\tau\)-approximate \v{C}ech cocycles} on its nerve. Hidden multi--component inconsistencies become \(k\)-simplices whose composite morphisms disagree beyond~\(\tau\). A Rust~+~Python prototype, nine documented outages, and a public benchmark plan support the thesis.

\bigskip

\section{Strengths}
\begin{tabular}{@{}c L{6.4cm} L{2.5cm}@{}}
\toprule
\textbf{ID} & \textbf{What \& Why it matters} & \textbf{Paper location} \\
\midrule
S--1 & \textbf{Real\hyp world motivation.} Outage corpus (Airbnb schema migration, Netflix feature flag, Meta embedding skew \ldots) shows pair--wise tests miss costly bugs. & \S3.1 \\
S--2 & \textbf{Solid theoretical footing.} Lawvere--enriched categories + \(\varepsilon\)-pseudoinverses give a principled tolerance model; soundness theorem and \(\mathcal O(e\,\Delta^{k-1})\) enumeration bound. & \S2.2 \\
S--3 & \textbf{Unified lens on disparate checks.} Drift, schema skew, fairness\hyp bias tracing all map to the same \(k\)-simplex consistency pattern under different norms. & \S2.3 \\
S--4 & \textbf{Reproducibility\hyp first.} Five--item artefact list (repo, data, Docker, CI, Zenodo DOI). & \S5 \\
\bottomrule
\end{tabular}

\section{Key Weaknesses / Open Questions}
\begin{longtable}{@{}c L{4.8cm} L{3.2cm} L{4.0cm}@{}}
\toprule
\textbf{Rank} & \textbf{Issue} & \textbf{Impact if unaddressed} & \textbf{Mitigation} \\
\midrule
\endhead
W--1 & \textbf{Acyclic--only theory.} Feedback loops (re\hyp training, online learning) excluded. & May deem scope too narrow for real pipelines. & Add temporal unrolling sketch; promise cyclic extension via traced monoidal categories. \\
W--2 & \textbf{Scalability of \(k\)-simplex enumeration.} Worst--case exponential in high\hyp fan\hyp out DAGs. & Could be labelled ``impractical''. & Report runtime on \(\ge 10\,\mathrm{k}\)-node DAG; entropy\hyp weighted sampling; early exit on first violation. \\
W--3 & \(\tau\) \textbf{calibration unclear.} Current Benjamini--Hochberg uses seeded bugs only. & ``Magic number'' criticism; risk of high FPR/FNR. & Provide rule\hyp of\hyp thumb (3\(\times\) median divergence) and Lipschitz bound; validate on real logs. \\
W--4 & \textbf{Empirical depth.} Only three public pipelines \& 20 seeded bugs. & ``Toy dataset'' critique. & Seek anonymised \(100\,\mathrm{k}\)-edge pipeline (Spotify/HF). Publish aggregated stats if NDA. \\
W--5 & \textbf{Dense category theory prose.} & Clarity score hit. & Add intuition box + running toy example; move proofs to appendix. \\
W--6 & \textbf{Baseline coverage incomplete.} & Novelty claim questioned. & Expand related\hyp work table; include incidents caught column. \\
\bottomrule
\end{longtable}

\section{Targeted Fixes and Insertions}
\begin{tabular}{@{}c L{7.2cm} L{2.8cm}@{}}
\toprule
\textbf{Patch ID} & \textbf{Description} & \textbf{Insert location} \\
\midrule
F--1 & Toy 3--node pipeline example capturing a 2\hyp simplex bug; side\hyp by\hyp side graph \& tensor diff. & new \S2.0 \\
F--2 & \(\tau\)-selection appendix: statistical, Lipschitz and empirical recipes; ablation plot. & App.~B \\
F--3 & Runtime table on DAGs of 1k, 10k, 80k nodes; effect of sampling and early exit. & \S4 Experiments \\
F--4 & Cyclic\hyp graph outlook via traced monoidal categories; cite Selinger~(2022). & \S6.1 \\
F--5 & Expanded related\hyp work Table covering Evidently AI, Databricks ``Quality Suite'', LinkedIn Autometry; add mathematics, guarantees, incidents columns. & \S3.2 \\
F--6 & Broader\hyp impact note on CI alert fatigue \& severity scoring. & \S7 \\
\bottomrule
\end{tabular}

\section{Re\hyp Scored Recommendation (Projected)}
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Criterion} & \textbf{Before} & \textbf{After fixes} \\
\midrule
Originality & 5 & 5 \\
Technical quality & 4 & 4.5 \\
Clarity & 3 & 4 \\
Significance & 4 & 4.5 \\
\midrule
\textbf{Overall} & 4 / 5 & \textbf{4.5 / 5 (Solid accept)} \\
\bottomrule
\end{tabular}

\section{Action Plan with Owners and Checkpoints}
\begin{longtable}{@{}c L{3.8cm} L{3.2cm} L{4.0cm}@{}}
\toprule
\textbf{Week} & \textbf{Deliverable} & \textbf{Owner} & \textbf{Success metric} \\
\midrule
\endhead
T+1 & Toy pipeline example and intuition box (F--1) & Alice & PR merged, CI green. \\
T+2 & \(\tau\)-calibration appendix + ablation plot (F--2) & Bob & KS test: FPR \(\le 5\%\). \\
T+3 & Runtime experiments on 80k--node DAG (F--3) & Chen & Runtime \(< 2\times\) streaming baseline. \\
T+3 & Related\hyp work expansion (F--5) & Dana & Table accepted in writing sync. \\
T+4 & Cyclic\hyp graph theory sketch (F--4) & Emily & Section approved by theory lead. \\
T+4 & Impact \& alert fatigue note (F--6) & Farid & \(\ge\)2 external reviewers find clear. \\
T+5 & External pipeline partnership results & PM team & NDA signed or fallback stats ready. \\
T+6 & Paper ``camera\hyp ready'' candidate; dry\hyp run rebuttal & All & Internal mock review \(\ge 4.3/5\). \\
\bottomrule
\end{longtable}

\section*{Final Note}
With these focused patches---especially empirical scale\hyp up and clearer exposition---Gerbe~AI is projected to move from a \emph{weak accept} to a \textbf{solid, broadly convincing contribution} at NeurIPS/ICML.

\end{document}

